---
title: "Agricola Exploration"
output: html_notebook
---

```{r}
library(rvest)
library(tidyverse)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
html <- read_html("http://www.boiteajeux.net/jeux/agr/historique.php?id=2990972")
```

```{r}
# Clean dirty html tags --------------------
clean_html <- function(html_string) {
  h <- gsub("<.*?>", "", html_string) # trim html tags
  h <- gsub("^[ \t]", "", h) # trim whitespace
  h <- gsub("\n", "", h)
  return(h)
}
```

Image processing dictionary
```{r}
imt <- tribble(
  ~french, ~english,
  "Mouton", "> sheep<",
  "Sanglier", "> boar<",
  "Boeuf", "> cow<",
  "Cereale", "> grain<",
  "Legume", "> veg<",
  "Bois", "> wood<",
  "Roseau", "> reed<",
  "Argile", "> clay<",
  "Pierre", "> stone<",
  "1stJ", "> starting player<",
  "PN", "> food<"
)
image_mapper <- pull(imt, english)
names(image_mapper) = pull(imt, french)
```


```{r}
player_history_raw <- map_df(1:15, function(round_num){
  round_html <- c(15:1)[round_num]
  if (round_num %% 2 == 1) {
    t <- html_nodes(html,
                    paste0('.clHistoFonce:nth-child(', round_html, ') .clHisto:nth-child(', i, ')'))
  } else {
    t <- html_nodes(html,
                    paste0('.clHistoClair:nth-child(', round_html, ') .clHisto:nth-child(', i, ')'))
  }
  # Get html text
  clean <- t %>%
    xml_contents() %>%
    html_text()
  
  res <- tibble(turn_num = as.numeric(str_extract(clean, "[0-9]+")),
                round_num = round_num,
                raw = t %>% xml_contents() %>% as.character())
  return(res)
})
player_history_raw
```

```{r}
player_history <- player_history_raw %>%
  mutate(trans = str_replace_all(raw, image_mapper)) %>%
  mutate(clean = clean_html(trans)) %>%
  mutate(clean = str_replace(clean, "[0-9]+", "")) %>%
  mutate(clean = str_replace(clean, "=&gt;", "yields")) %>%
  filter(!is.na(turn_num)) %>%
  arrange(turn_num) %>%
  select(turn_num, round_num, clean)
player_history
```

Add player name and num, create whole game.
```{r}

```

